Research Proposal

### 2021-10-05 Reports/JOURNAL - Confidence Regions/ResearchProposal.tex
Update ResearchProposal.tex

We already have purely empirical results about the confidence region of points in the $H\times C$ plane under white noise.
In this work, we propose advancing such a knowledge by using a general model for discrete distributions.

@@

\begin{itemize}
\item[Q1:] What is the distribution of $(\mathfrak{H},\mathfrak{C})$ under $H_0:\mathcal X\text { is white noise}$?
\begin{itemize}
	\item $\bm X = (X_1,X_2,\dots,X_N)$ is white noise
	\item Fix $\tau=1$ and define $D$
	\item $\bm \pi=(\pi_1,\pi_2,\dots,\pi_{n-D})$ is the random sequence of patterns from $\bm X$. There are $D!$ possible patterns.
	\item The patterns are not independent because some cannot follow others, but we may shuffle them to avoid such restriction.
	\item $\bm h$ is the random histogram of proportions from $\bm \pi$
	\item $(\mathfrak{H},\mathfrak{C})$ is the random point in the Entropy-Complexity plane computed from $\bm h$
	\begin{itemize}	
		\item $H^*$ is the operator that transforms the random vector $\bm h$ into the random variable $\mathfrak{H}$
		\item $C^*$ is the operator that transforms the random vector $\bm h$ in to the random variable $\mathfrak{C}$
		\item Notice that $H^*$ does not compute the entropy of $\bm h$, which is a fixed value; it produces a random variable from the random variable $\bm h$. The same holds for $C^*$; it does not compute the complexity.
	\end{itemize}
\end{itemize}
\item[Q1:] What is the distribution of $
	(\mathfrak{H},\mathfrak{C}) = 
	\big(H^*(\bm h),C^*(\bm h)\big)$? Under $H_0$, $\bm h$ is (?) a collection of iid random variables taking values in $\{1, 2,\dots, D!\}$ with same probability $1/D!$ but, as they form a histogram, there must be a restriction on the sum of their values. I don't know how to go on from this point. Multinomial? Whichever the distribution of $\bm h$, how do we compute the distribution of $H^*(\bm h)$?
\item[$\bullet$] Alternatively, instead of considering such a flexible discrete distribution, we may use a parametric model.
\item[Q2:] What is the distribution of $
(\mathfrak{H},\mathfrak{C}) = 
\big(H^*(\bm h),C^*(\bm h)\big)$ when $\bm h\sim\text{db}(\alpha,\beta,1, D!)$?
\item[] But we go back to a quantity, rather than to a random variable.
\item[Q3:] Assume we have been able to compute the quantities $H^*(\alpha,\beta)$ and $C^*(\alpha,\beta)$ under the $\text{db}(\alpha,\beta,1, D!)$ model.
\item[] We have the maximum likelihood estimator for $(\alpha,\beta)$, say $(\widehat\alpha,\widehat\beta)$.
\item[] We know that the asymptotic distribution of $(\widehat\alpha,\widehat\beta)$ is a bivariate Gaussian law.
\item[] How close are we to finding an approximate distribution for $
(\mathfrak{H},\mathfrak{C})$ under $H_0$?
\end{itemize}

>>>>

We already have purely empirical results about the confidence region of points in the $H\times C$ plane under white noise.
In this work, we propose advancing such a knowledge by using a general model for discrete distributions.
The work by \citet{OrdinalPatternProbabilities} is among the few that study theoretical (distributional) properties of these points; the article proves consistency and asymptotic normality of estimators.

@@

\begin{itemize}
\item[Q1:] What is the distribution of $(\mathfrak{H},\mathfrak{C})$ under $H_0:\mathcal X\text { is white noise}$?
\begin{itemize}
	\item $\bm X = (X_1,X_2,\dots,X_N)$ is white noise
	\item Fix $\tau=1$ and define $D$
	\item $\bm \pi=(\pi_1,\pi_2,\dots,\pi_{n-D+1})$ is the random sequence of patterns from $\bm X$. There are $D!$ possible patterns.
	\item The patterns are not independent because some cannot follow others, but we may shuffle them to avoid such restriction.
	\item $\bm h$ is the random histogram of proportions from $\bm \pi$
	\item $(\mathfrak{H},\mathfrak{C})$ is the random point in the Entropy-Complexity plane computed from $\bm h$
	\begin{itemize}	
		\item $H^*$ is the operator that transforms the random vector $\bm h$ into the random variable $\mathfrak{H}$
		\item $C^*$ is the operator that transforms the random vector $\bm h$ in to the random variable $\mathfrak{C}$
		\item Notice that $H^*$ does not compute the entropy of $\bm h$, which is a fixed value; it produces a random variable from the random variable $\bm h$. The same holds for $C^*$; it does not compute the complexity.
	\end{itemize}
\end{itemize}
\item[Q1:] What is the distribution of $
	(\mathfrak{H},\mathfrak{C}) = 
	\big(H^*(\bm h),C^*(\bm h)\big)$? Under $H_0$, $\bm h$ is (?) a collection of iid random variables taking values in $\{1, 2,\dots, D!\}$ with same probability $1/D!$ but, as they form a histogram, there must be a restriction on the sum of their values. I don't know how to go on from this point. Multinomial? Whichever the distribution of $\bm h$, how do we compute the distribution of $H^*(\bm h)$?
\item[$\bullet$] Alternatively, instead of considering such a flexible discrete distribution, we may use a parametric model.
\item[Q2:] What is the distribution of $
(\mathfrak{H},\mathfrak{C}) = 
\big(H^*(\bm h),C^*(\bm h)\big)$ when $\bm h\sim\text{db}(\alpha,\beta,1, D!)$?
\item[] But we go back to a quantity, rather than to a random variable.
\item[Q3:] Assume we have been able to compute the quantities $H^*(\alpha,\beta)$ and $C^*(\alpha,\beta)$ under the $\text{db}(\alpha,\beta,1, D!)$ model.
\item[] We have the maximum likelihood estimator for $(\alpha,\beta)$, say $(\widehat\alpha,\widehat\beta)$.
\item[] We know that the asymptotic distribution of $(\widehat\alpha,\widehat\beta)$ is a bivariate Gaussian law.
\item[] How close are we to finding an approximate distribution for $
(\mathfrak{H},\mathfrak{C})$ under $H_0$?
\end{itemize}
